Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-16 bdcloud_paper/latex/paper.tex
starting adding references

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Domain-Driven Generative Data Model for BigPetStore}

@@

\emph{Ab initio} mathematical models for generating synthetic data overcomes several of these obstacles.  The code for generating the data is often small, enabling free hosting, licensing restrictions are often avoided, and the data size can be scaled, enabling seamless usage of the same data set across a range of scenarios.  Common synthetic data set generators such as TeraGen and the Intel Hadoop Benchmark \textcolor{red}{reference} can generate data sets quickly and at any scale, but they are over-specialized for benchmarking, resulting in semantically-void data that lacks usefulness for analytics examples. The lack of frameworks for generating semantically-rich data at arbitrary scale denies developers access to consistent data sets that can be used across a range of environments \textcolor{red}{Huppler, Pavlo}.

@@

The BigPetStore application aims to be a big data application blueprint built around a fictional chain of pet stores, which incorporates a data generator and complex examples of cleaning, aggregation, and analytics using well-known tools such as Hive and Mahout from across the Hadoop and Spark ecosystems \textcolor{red}{reference}. BigPetStore's usefulness has been demonstrated by its incorporation into the Apache BigTop distribution for testing and as a reference application \textcolor{red}{reference}.

@@

where $a_i$ is the amount of item category $i$ ``stuff'' remaining at time $t$. The variable $u_i$ gives the average usage rate and $\sigma^2_i$ gives the variance of the usage rate for item category $i$. The SDE is numerically integrated using the Euler-Maruyama method \textcolor{red}{reference} with timestep $\Delta t_n$ sampled from a Poisson process:

@@

The proposed transaction time is accepted if $p(t=T_T) < r$, where $r \sim \text{U}(0, 1)$. Until the proposed transaction time is accepted, a new proposed transaction time is generated by sampling new offset times. If the proposed transaction time is accepted, the shopping cart of items is generated through a separate simulation discussed below. Transactions are generated until the accepted transaction time is later than the end time given as a simulation parameter.

@@

\section{Implementation}
The models and simulations were implemented using Python. The source code is available on GitHub \textcolor{red}{reference} at \url{https://github.com/rnowling/bigpetstore-data-generator} under the Apache 2 license.

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
%\subsection{Subsection Heading Here}
%Subsection text here.

%\subsubsection{Subsubsection Heading Here}
%Subsubsection text here.
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Domain-Driven, Generative Data Model for BigPetStore}

@@

\emph{Ab initio} mathematical models for generating synthetic data overcomes several of these obstacles.  The code for generating the data is often small, enabling free hosting, licensing restrictions are often avoided, and the data size can be scaled, enabling seamless usage of the same data set across a range of scenarios.  Common synthetic data set generators such as TeraGen and the Intel Hadoop Benchmark \textcolor{red}{reference} can generate data sets quickly and at any scale, but they are over-specialized for benchmarking, resulting in semantically-void data that lacks usefulness for analytics examples. The lack of frameworks for generating semantically-rich data at arbitrary scale denies developers access to consistent data sets that can be used across a range of environments \textcolor{red}{Huppler, Pavlo}.  \textcolor{red}{standard benchmarks}

@@

The BigPetStore application aims to be a big data application blueprint built around a fictional chain of pet stores, which incorporates a data generator and complex examples of cleaning, aggregation, and analytics using well-known tools such as Hive and Mahout from across the Hadoop and Spark ecosystems \textcolor{red}{reference}. BigPetStore's usefulness has been demonstrated by its incorporation into the Apache BigTop distribution \cite{BigTop} for testing and as a reference application.

@@

where $a_i$ is the amount of item category $i$ ``stuff'' remaining at time $t$. The variable $u_i$ gives the average usage rate and $\sigma^2_i$ gives the variance of the usage rate for item category $i$. The SDE is numerically integrated using the Euler-Maruyama method\cite{Klouden13} with timestep $\Delta t_n$ sampled from a Poisson process:

@@

The proposed transaction time is accepted if $p(t=T_T) < r$, where $r \sim \text{U}(0, 1)$. Until the proposed transaction time is accepted, a new proposed transaction time is generated by sampling new offset times. If the proposed transaction time is accepted, the shopping cart of items is generated through a separate simulation discussed in Section~\ref{sec:transaction-purchases} below. Transactions are generated until the accepted transaction time is later than the end time given as a simulation parameter.

@@

\section{Implementation}
The models and simulations were implemented using Python. The source code is available on GitHub \cite{GitHub} at \url{https://github.com/rnowling/bigpetstore-data-generator} under the Apache 2 license.

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
\bibliographystyle{plain}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,paper}
\bibliography{paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
%\begin{thebibliography}{1}

%\bibitem{IEEEhowto:kopka}
%\subsection{Subsection Heading Here}
%Subsection text here.

%\subsubsection{Subsubsection Heading Here}
%Subsubsection text here.
%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

%\end{thebibliography}
